---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ST.Colours

<!-- badges: start -->
<!-- badges: end -->

The goal of ST.Colours is to create an accessible and vibrant package for data visualization.

## Installation

You can install the development version of ST.Colours like so:

``` r
# install.packages("devtools")
devtools::install_github("TolaniRuthOgun/ST.Colours")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(palettes)
library(ggplot2)
library(scales)
library(ST.Colours)
ggplot(data.frame(x = rnorm(10000), y = rnorm(10000)), aes(x = x, y = y)) +
  geom_hex() + coord_fixed() + scale_fill_palette_b(ST.Colours$Purple) 

```


Using ST.Colours with other packages (by https://github.com/mccarthy-m-g)
- [Using palettes with ggplot2](https://mccarthy-m-g.github.io/palettes/articles/ggplot2.html)
- [Using palettes with gt](https://mccarthy-m-g.github.io/palettes/articles/gt.html)
- [Using palettes with biscale](https://mccarthy-m-g.github.io/palettes/articles/biscale.html)
- [Compatibility with other colour packages](https://mccarthy-m-g.github.io/palettes/articles/compatibility.html)

##Included Palettes

```{r }
plot(ST.Colours::ST.Colours)
```
ST.Colours comes with a set of `r length(ST.Colours_discrete)` discrete colour palettes, and `r length(ST.Colours_sequential)` sequential colour palettes, which can be accessed from the following R objects:

- `ST.Colours_discrete` for discrete palettes
- `ST.Colours_sequential` for sequential palettes
- `ST.Colours` for all palettes

To preview the palettes in the console simply print them:

```{r asciicast ST.Colours_discrete}
ST.Colours_discrete
```

To preview the palettes in the Plots pane use `plot()`:

```{r ST.Colours_sequential}
plot(ST.Colours_sequential)
```



Palettes can be subset using `[`, `[[`, and `$`.

  - To extract one or more palettes use `[`:

```{r asciicast extract-palette}
    ST.Colours_sequential[c("Teal", "Coral")]
```
  
  - To extract a single palette as a colour vector use `[[` or `$`:

    ```{r asciicast extract-vector-1}
    ST.Colours_sequential[["Teal"]]
    ```
    
    ```{r asciicast extract-vector-2}
    ST.Colours_sequential$Purple
    ```
    
  - To get names of palettes use `names()`:

    ```{r}
    names(ST.Colours_sequential)
    ```

## Documentation

See also documentation for the palettes package at [`https://mccarthy-m-g.github.io/palettes/`](https://mccarthy-m-g.github.io/palettes/reference/index.html) or in the installed package: `help(package = "palettes")`.

## License

CC0

